### 2020-04-19 Case Studies/02_race-times.rmd
cherry blossom work
cherry blossom work

summary(as.numeric(ages))

@@

```{r}
years <- 1999:2012

res <- sapply(years, FUN = function(year){

   print(paste("loading year...", year))

   file <- read_results("men", year)

   parsed <- extractVariables(file)
})

file <- read_results("men", 2006)
m2006 <- extractVariables(file)

age <- m2006[, "home"]

sum(is.na(age))

n <- length(file)

file[n]

m2001$ag

@@

mfilenames <- file.path(data.dir, paste("men_txt/", 1999:2012, ".txt", sep = ""))
menFiles <- lapply(mfilenames, readLines)
names(menFiles) <- 1999:2012

menResMat <- lapply(menFiles, extractVariables)

length(menResMat)
sapply(menResMat, nrow)
```

@@

menDF <- mapply(createDF, menResMat, year = years,
                sex = rep("M", 14), SIMPLIFY = F)

>>>>

summary(as.numeric(vars))

@@

@@

@@

years <- 1999:2012
menDF <- mapply(createDF, menResMat, year = years,
                sex = rep("M", 14), SIMPLIFY = F)
